High-Performance Data Analysis on JANUS using Apache Spark

### 2013-12-18 paper.tex
s/Janus/JANUS/ and conclusion blurb

\title{High-Performance Data Analysis on Janus using Apache Spark}
\author{Nick Vanderweit \\
        Ning Gao \\
        Anitha Ganesha \\
        Michael Kasper}

@@

\section{Evaluation}
We conducted our evaluation of the Spark system on the University of
Colorado's Janus supercomputer. Janus consists of 1,368 nodes, each containing
two six core Intel Xeon Westmere-EP chips at 2.8 GHz, for a total of 12 cores
per node. Additionally, each core has 2 GB of 1333 MHz DDR RAM, for a total of
24 GB per node \citep{tufo}. In our research, we employed Spark version
0.8.0 along with Scala version 2.9.3. During our testing of the Spark system,
we access input files from Janus' lustre distributed file system. Our aim was
to assess the Spark runs on Janus and determine optimal configurations to
achieve the best performance.

@@

Ten trials were performed for each test, allows us to compute average
runtimes. To compute the speedup, Spark runtimes were compared to the UNIX grep
command's serial runtime on the same file. Finally, during our first test on the
20 GB file, we evaluated performance using a different number of workers per
node. In Spark, a worker is an executor with it's own JVM which processes it's
own portion of the distributed data set. By default, a single worker is
employed on each node. For this test, we wanted to see if this was the ideal
setting for running Spark on Janus.

@@

\section{Conclusion}

>>>>

\title{High-Performance Data Analysis on JANUS using Apache Spark}
\author{Nick Vanderweit \\
        Ning Gao \\
        Anitha Ganesha \\
        Michael Kasper}

@@

\section{Evaluation}
We conducted our evaluation of the Spark system on the University of
Colorado's JANUS supercomputer. JANUS consists of 1,368 nodes, each containing
two six core Intel Xeon Westmere-EP chips at 2.8 GHz, for a total of 12 cores
per node. Additionally, each core has 2 GB of 1333 MHz DDR RAM, for a total of
24 GB per node \citep{tufo}. In our research, we employed Spark version
0.8.0 along with Scala version 2.9.3. During our testing of the Spark system,
we access input files from JANUS' lustre distributed file system. Our aim was
to assess the Spark runs on JANUS and determine optimal configurations to
achieve the best performance.

@@

Ten trials were performed for each test, allows us to compute average
runtimes. To compute the speedup, Spark runtimes were compared to the UNIX grep
command's serial runtime on the same file. Finally, during our first test on the
20 GB file, we evaluated performance using a different number of workers per
node. In Spark, a worker is an executor with it's own JVM which processes it's
own portion of the distributed data set. By default, a single worker is
employed on each node. For this test, we wanted to see if this was the ideal
setting for running Spark on JANUS.

@@

\section{Conclusion}
We found that, while Spark offers an appealing abstraction layer for
data-parallel programming, achieving reasonable scalability even on trivial
problems is still very difficult. Without adequate profiling tools, we found
ourselves puzzled by the lackluster results of our experiments. With more time,
we could probably use the Spark logs to better understand where our serial
bottlenecks are and increase efficiency. It may very well still be worth
exploring how Spark could be used on JANUS, but it may require rethinking
how we are using the network and filesystems for this task.
